The Community Land Model, version 5.1 \\ One-at-a-time Parameter Perturbation Ensemble

### 2023-10-12 ms/ms.tex
Updates from Overleaf

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/bar.pdf}
\caption{193 parameters were perturbed across the various domains of the land model.}
\label{fig:params}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=30pc]{../figs/sims.pdf}
\caption{The approximate number of simulations afforded by 1 million core-hours on the Cheyenne supercomputer for a range of CLM configurations. Configurations are labeled according to spin-up procedure (CN-matrix or the standard 1500-year spinup) and horizontal resolution (`sg' signifies sparsegrid). The inset map shows the locations of the 400 sparse grid cells. See Section \ref{methods} for spin-up and sparsegrid details.}
\label{fig:sims}
\end{figure}

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/main/bar.png}
\caption{193 parameters were perturbed across the various domains of the land model.}
\label{fig:params}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=30pc]{../figs/main/sims.png}
\caption{The approximate number of simulations afforded by 1 million core-hours on the Cheyenne supercomputer for a range of CLM configurations. Configurations are labeled according to spin-up procedure (SASU or the standard 1500-year spinup) and horizontal resolution (`sg' signifies sparsegrid). The inset map shows the locations of the 400 sparse grid cells. See Section \ref{methods} for spin-up and sparsegrid details.}
\label{fig:sims}
\end{figure}
